---
title: "W_UP_01"
author: "Maximiliano ortiz"
date: "fall 2025"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
boxplot(pushups~position,data=mydata)
```
  
The first quartile of the "skill" players is bigger than the third quartile of the "Line" players. I believe that what Dr.k told us that in these situations there will be a statistical difference and that's what I think I'll observe.  

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```

I observed that there is a total of 8 "Line" players and 22 "skill" players. The average number that a "Line" player can do is 17.12500 pushups, while the "Skill" players can do an average 49.72727 pushups. 	

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
t.test(pushups~position,data=mydata)
```

The chances of getting the results like this if there is no difference in means between group "Line" and "Skill" is equal to .000009421. Such a really low p-value like that allowed me to concluded that there really is a big margin between "Line" players and "Skill" players.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

In this write up I learned how to plug in data whether it's a box plot, favstats, or t-test. I was able to observe all numerical data. For example in the Box plot chart I was able to analyse that the "Skill" players could do more push ups than the "Line" players because the "Skill" players had a bigger first quartile that the "Line" players third quartile. Another example would be in the favstats where I got all the exact number of players and there average. The "Skill" players average was higher than the "Line players average. Lastly in the T-test I got the P-value which was really low and it showed the big margin between "Skill and "Line" players. This is what I learned in this write up today.   